Generate data for NOBA cod ensemble modeling

### 2020-03-23 NOBAcod.Rmd
full age test for cod with code folding

---
title: "Generate data for NOBA cod ensemble modeling"
author: "Sarah Gaichas"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

@@

@@

Does it work?

@@

numsage <- load_nc_annage(dir = d.name,
                  file_nc = file_nc,
                  bps = bps,
                  fgs = fgs,
                  biolprm = biolprm,
                  select_groups = select_groups,
                  select_variable = "Nums",
                  check_acronyms = TRUE,
                  bboxes = boxes)
  if(verbose) message("Numbers read in from ANNAGEBIO.")

weightage <- load_nc_annage(dir = d.name,
                  file_nc = file_nc,
                  bps = bps,
                  fgs = fgs,
                  biolprm = biolprm,
                  select_groups = select_groups,
                  select_variable = "Weight",
                  check_acronyms = TRUE,
                  bboxes = boxes)
  if(verbose) message("Weight read in from ANNAGEBIO.")

@@

Need to aggreagate these to see if they look reasonable

@@

  #numbers based fishery independent survey for age and length comps
  # same user specifications as indices
  survey_N <- atlantisom::create_survey(dat = numsage,
                                        time = survtime,
                                        species = select_groups,
                                        boxes = survboxes,
                                        effic = surveffic,
                                        selex = survselex)
  #Sample fish for age composition
  # if we want replicates for obs error this sample function will generate them
  age_comp_data <- list()
  for(i in 1:n_reps){
    age_comp_data[[i]] <- atlantisom::sample_fish(survey_N, surveffN)
  }

    # save age comps
  if(save){
    saveRDS(age_comp_data, file.path(d.name, paste0(scenario.name, "survObsFullAgeComp.rds")))
  }

>>>>

---
title: "Generate data for NOBA cod ensemble modeling"
author: "Sarah Gaichas"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_fold: hide
---

@@

# WARNING!! comment above and use this for annage output
survselex <- data.frame(species=rep(survspp, each=n_annages),
                        agecl=rep(c(1:n_annages),length(survspp)),
                        selex=rep(1.0,length(survspp)*n_annages))

@@

Does it work? This snippet will go into `run_truth` if it does:

@@

numsage <- load_nc_annage(dir = d.name,
                  file_nc = file_nc,
                  bps = bps,
                  fgs = fgs,
                  biolprm = biolprm,
                  select_groups = select_groups,
                  select_variable = "Nums",
                  check_acronyms = TRUE,
                  bboxes = boxes, 
                  verbose = TRUE)
  #if(verbose) message("Numbers read in from ANNAGEBIO.")

weightage <- load_nc_annage(dir = d.name,
                  file_nc = file_nc,
                  bps = bps,
                  fgs = fgs,
                  biolprm = biolprm,
                  select_groups = select_groups,
                  select_variable = "Weight",
                  check_acronyms = TRUE,
                  bboxes = boxes, 
                  verbose = TRUE)
  #if(verbose) message("Weight read in from ANNAGEBIO.")

@@

Need to aggreagate these to see if they look reasonable; this code snippet from `om_comps` with `numsage` output subsituted for `nums`.

@@

  #numbers based fishery independent survey for age and length comps
  # same user specifications as indices
  survey_N <- atlantisom::create_survey(dat = numsage,
                                        time = survtime,
                                        species = survspp,
                                        boxes = survboxes,
                                        effic = surveffic,
                                        selex = survselex)
  #Sample fish for age composition
  # if we want replicates for obs error this sample function will generate them
  age_comp_data <- list()
  for(i in 1:n_reps){
    age_comp_data[[i]] <- atlantisom::sample_fish(survey_N, surveffN)
  }

    # save age comps
  #if(save){
    saveRDS(age_comp_data, file.path(d.name, paste0(scenario.name, "survObsFullAgeComp.rds")))
  #}

Plot full age comps, have 20 years for cod now, no longer age class but annual ages.

```{r plotfullagecomp}

#read in comp data
age_comp_data <- readRDS(file.path(d.name, paste0(scenario.name, "survObsFullAgeComp.rds")))
age_comp_data <- age_comp_data[[1]]

#fish_age_comp <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsAgeComp.rds")))
#fish_age_comp <- fish_age_comp[[1]]

#add this to om_indices function so that this has years when read in
#fish_age_comp$time <- as.integer(floor(fish_age_comp$time/fstepperyr))

  Natageplot + facet_wrap(~time/stepperyr, ncol=6, scales="free_y")

What is the weight output? Documentation only mentions numbers output. Looks like average weight at age for each time and polygon? If so, need to do weighted average weight using the numbers at age in each polygon?

```{r}
